### 2025-04-17 mixed-models.qmd
20250417 - cross-references

[Scatterplots](#sec-scatterplot) are a helpful tool for quickly examining the association between two variables.
However, [scatterplots](#sec-scatterplot)—as well as correlation and multiple regression—can hide meaningful associations that differ across units of analysis.

>>>>

[Scatterplots](#sec-scatterplot) are a helpful tool for quickly examining the association between two variables.
However, [scatterplots](#sec-scatterplot)—as well as [correlation](#sec-correlation) and [multiple regression](#sec-multipleRegression)—can hide meaningful associations that differ across units of analysis.
